Adopting agile in the large: motivations, success factors and challenges

### 2014-05-08 journal/article.tex
Analysis; Work in progress

WORKING IN SILOS --> Certain expertise is required in many places

* Teams were reorganized without notice --> Planning was hampered when people did not konw who would stay on a team
* Frequent changes --> People managers had to agree to minimize team changes
[P11]
When we launched multiple Scrum teams, we tried to keep existing teams together
and form new teams based on skills.  As we gained experience, we realized that
there were skills shortages in certain types of expertise that wasn’t possible
to develop in a sprint or two. There was pressure to move engineers with certain
skills to the teams that needed them for work on upcoming sprints or to address
critical customer requirements.  When moves occurred without much notice, teams
couldn’t plan effectively if they didn’t know who would stay on a team.  After
several months of frequent changes, product owners and people managers agreed to
minimize team changes, and even talked of instituting a “trading deadline.”

>>>>

("C: Part of organization is in old mindset" | "C: Using old and new models side-by-side")

* The agile model had to made fit in the context of the entire enterprise
* There were old projects using existing approaches
* General challenge of organizing
[P8]
The final concern was to align the agile delivery processes with the
pre-existing delivery model in use at ABC Bank. Not only were many projects
already in-flight using existing development approaches, but also many new
projects would be a blend of traditional and agile approaches. A clear
relationship to the existing delivery approaches was essential.

* Bottom up transformation
* Corporate level --> Use of waterfall
* There was tension built up between these approaches --> within teams --> in management
* Problems --> Generic ``problems'' --> Particularly when collaborating with external teams
* An inception sprint --> Some sees as necessary --> Others consider as failing in iterativeness --> Possible to avoid being agile
[P10]
at a corporate level Yahoo! still embraced a more traditional (top-down,
heavy-weight, big design up front, waterfall) product development process (known
rather unimaginatively as PDP). The tension between these two approaches – and a
corresponding confusion – began to show up at all levels within the company –
within the sprint teams themselves, within the leadership of organizations such
as Music, and particularly when teams from different organizations were
attempting to collaborate on products while using  fundamentally different
approaches to develop them.

The sometimes awkward co-existence of agile and traditional product lifecycles
continues to be a challenge at Yahoo!  For instance, one hotly contested
concession to the ‘big design up front’ mentality was to accommodate a ‘Sprint
0’ of indeterminate length that would allow for some of the more traditional
planning, specification and design activities to be completed.  In the minds of
some, this was a necessary bridge between the sprint-focused world of scrum and
the traditional domain of portfolio management and organizational planning.  In
the minds of many, however, the ‘Sprint 0’ stipulation struck at the heart of
what it meant to iteratively refine an emergent solution within the agile
process, and  in some cases it allowed teams and individuals to avoid being
agile at all by relegating all their work to this formation sprint.

* People are pulled off to fight fires (old commitments?)
[P17]
Within the first two iterations the pilot teams saw every common impediment to
producing fully-tested software in rapid iterations – team members were pulled
off project to fight fires; architectural blocks arose due to multiplexed
resources; there was inadequate access to product owners; and development teams
were spread across as many as four cities.

* Management requires increasing documentation --> Extra burden on agile teams
[P20]
The documentation requirements were driven basically from the upper management,
ISO certificate requirements and the traditional development method that is
currently used. Although agile development promises sufficient documentation of
the projects, it didn’t seem very convincing to the upper management when they
end up receiving few documents in comparison with the previous model of
documentation.
Many attempts were made to balance between the upper management requirement
regarding documentation and between adopting Scrum method. Agile teams started
increasing the number of documents required for documentation and started to
customize Scrum as much as possible to conform with all the upper management
requirements of documentation norms.
This did not work very well and it created extra burden on the agile teams.

* The Scrum team was forced to comply with approval procedures --> unnecessary work
[P21]
The traditional method currently in S was customized to comply with the
governmental system of other department. The new agile method being introduced,
Scrum, is developed in such highly bureaucratic environment. The agile team has
to secure approvals and signatures before moving from one step to another. This
was perceived by the team members as unnecessary and more time was taken into
account to develop a new project.
The scrum method requires much less correspondence, less time in communication
between customer and the team and requires significantly less paper work and
approvals as the customer is supposed to be involved in every step. Here, the
governmental bureaucratic system came on the way of succeeding in the adoption
of agile.

* Generic problem: Synchronizing with the waterfall program
[P26]
Using scrum only on the team level had led to additional problems. Software
interfaces were not properly synchronized with other development teams.
Larger features were causing synchronization problems due to dependencies in
code. Synchronization to the main waterfall program was considered problematic.
Deploying scrum on the team level had brought flexibility in the team, but the
ability to embrace the change was not truly benefiting the whole program as it
was lacking capabilities to systematically embed the changes in all teams and
levels.

* Teams were forced to work for several programs in parallel
* Working in this way revealed that overloading of tasks was problematic
[P26]
For practical reasons, some scrum teams needed to work for several programs.
Sharing resources has not been seen as a good option by the programs, as it
results in non-steady output level and makes estimation harder.
Programs with less dedicated resources have not made very good progress. In
fact, agile program model deployment has revealed the overload of tasks to
programs and teams and the true development velocity and capability.

Comment:
"Programs" or "program model is seen as the "old model" here. I am not entirely
sure whether that was the "old model" or was it just planned like this --
problematic from the start.

* A mix of processes --> WaterScrum
* Problem --> The entire organization can impossibly change at once
* Problem --> Additional coordination necessary
[P29]
Many groups manage 50+ applications and at any given time, over half are in some
stage of development or modification.  With complex technical, scheduling, and
requirements interdependencies, implementing Scrum beyond a limited pilot
present other challenges.  Today, it is not feasible to stop all systems to
retool our processes.  We are essentially forced to “change the tires on a
moving car”.
We are currently examining various models for dealing with what we call
“WaterScrum” - simultaneously managing co-dependent waterfall and SCRUM projects
together 1 .  WaterScrum is like trying to play two sports on the same field at
the same time.  Extra coordination is necessary to make it work.

* Mixing agile and waterfall --> Waterfall projects needed design aspects up front but agile teams created design incrementally throughout the project
[P29]
However, one key issue arose that was not fully anticipated: the waterfall
project would need to complete its design phase before LPO had completed all of
their sprints, and because the Scrum project was incremental, some design
aspects for later sprints would not be complete until after the waterfall
project design complete milestone.  This mixture caused some temporary grief.

* Old mindset
* Management in watterfall mindset --> Suspicion when percentage complete is missing
* Management wanted also fixed delivery dates and cost analysis
* Development messed up --> Deliverable product not available after each iteration
[P35]
Management were used to the waterfall model project plans and lost confidence as
they could not determine the percentage ofwork completed and what stage gate
they were at. Management was also used to a delivery date, costs analysis and
statistics on progress being presented however this was also not available. From
the development and project planning perspective a deliverable product after
each iteration was not available. Had one been available it would have restored
management’s confidence.

* Generic problems --> Management is traditionally oriented
* Management failed to change --> Phasing out
* Problem: Big up front oriented management --> Managing to plans
[P38]
Sadly not all of the people and roles were able to adapt to the changing
environment. The most notable was the project management group. The group had
been very traditionally oriented. They focused on meetings and big up front
project plans. They managed to the plan, often competing with each other for
resources. When much of the responsibility shifted to the product owner and team
to formulate the plan, the project managers struggled to adjust.
Six months into the transformation it was becoming apparent that the project
management was continuing to have trouble adding value to the team. A tough
decision had to be made and the CTO met with the rest of management and they
decided to phase out the four project manager positions and create a new role on
the teams called delivery leads.

* Using old language to make agile familiar --> People get confused --> Nothing will change
* Mapping agile to the old model
[P44]
Use the established agile language. Many organizations, in their efforts to
adopt new techniques, try to soften the blow by adapting the language to
something more familiar in the culture. This could be a mistake when
implementing agile. Its language differs from what we know and recognize in
traditional development, but using the new language forces people to think in
new ways and helps foster creativity. If you change the agile language to match
what was previously known, people tend to slip back into their old ways.

* General problems with working with other teams --> Scrum teams considered unrealiable
[P45]
What could not be mitigated were issues with teams dependent on “unreliable”
Scrum teams, at least if the Scrum teams were isolated in a non-Scrum
environment. Scrum teams working jointly on a particular software product rarely
had complaints about unreliable delivery because they were familiar with the
Scrum methodology and figured out how to get their requirements added to other
teams’ backlogs and with the right priorities.

* Problem: Teams had to fill out forms of two processes --> New process seen as overhead
[P48]
The new practices, language, and delivery of increments – these things just
worked. Besides the good news, though, we also got a share of bad news. First,
Scrum was perceived to produce lots of overhead and due to the phase
implementation, sometimes both old and new templates and processes had to be
used.  Second, many teams thought Scrum was all about managing the tool, and
information was stored in multiple locations but not matching.

There is a certain amount of truth in the first complaint. The mismatch between
program management using the existing tools to manage and report on the program
and the teams using the new agile toolset contributed greatly to the additional
overhead.
